Effects of rotation and magnetic braking on Li abundances for solar-type stars

### 2019-08-21 project/overleaf/paper.tex
Paper v3.2.1
Increment graphic font sizes

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip, width=\columnwidth]{figures/li_var_vel_0_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The solid black line represents the reference model according to \citet{Choi2016}. The rest of lines are models which include PMS rotation with $\Omega / \Omega_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/li_var_vel_0_0g_z1.eps}
    \caption {Similar to figure (\ref{fig:li_var_vel_0g}) but zooming in on the ZAMS. The models with a higher initial rotational velocity reach already the ZAMS with a lower amount of Li measure on the star surface.}
    \label{fig:li_var_vel_0g_z1}
\end{figure}

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_0_0g.eps}
    \caption{The evolution of angular velocity at surface (solid line) and the top (dashed line) and bottom (dotted line) limits of the uppermost convective zone, as a function of time for several 1 $M_{\sun}$ models. The models includes PMS rotation with $\Omega / \Omega_{crit}$ values between 0.0084 and 0.0336. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed vertical lines make reference to the ZAMS.}
    \label{fig:rot_vel_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/hr_var_vel_0_0g_z1.eps}
    \caption{An example solar 1$M_{\sun}$ grid of stellar evolutionary track from PMS till TAMS covering a wide range of angular velocities. The rotation is activated in the models in the PMS and those models reach before the ZAMS and at a lower $T_{eff}$ than the non-rotating one (solid black line). The luminosity is expressed in terms of $L_{\sun}$}.
    \label{fig:hr_var_vel_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/li_var_vel_4_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $\Omega / \Omega_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_4_0g}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_0_0g.eps}
    \label{fig:subim1}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_3_5g.eps}
    \label{fig:subim2}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_4_0g.eps}
    \label{fig:subim3}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_4_5g.eps}
    \label{fig:subim4}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_5_0g.eps}
    \label{fig:subim5}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_5_5g.eps}
    \label{fig:subim6}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $\Omega / \Omega_{crit}$ varies between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
\label{fig:grid_li_var_vel}
\end{figure*}
\par

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0084_var_g.eps}
    \label{fig:subim21}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_014_var_g.eps}
    \label{fig:subim22}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0196_var_g.eps}
    \label{fig:subim23}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_028_var_g.eps}
    \label{fig:subim24}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 40mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0336_var_g.eps}
    \label{fig:subim25}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim26}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which $\Omega / \Omega_{crit}$ has been fixed and the magnetic field with intensity varies between $3.5\,G$ and $5.5\,G$, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
\label{fig:grid_li_var_g}
\end{figure*}

>>>>

\begin{figure}
	\includegraphics[trim = 35mm 15mm 20mm 15mm, clip, width=\columnwidth]{figures/li_var_vel_0_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The solid black line represents the reference model according to \citet{Choi2016}. The rest of lines are models which include PMS rotation with $\Omega / \Omega_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/li_var_vel_0_0g_z1.eps}
    \caption {Similar to figure (\ref{fig:li_var_vel_0g}) but zooming in on the ZAMS. The models with a higher initial rotational velocity reach already the ZAMS with a lower amount of Li measure on the star surface.}
    \label{fig:li_var_vel_0g_z1}
\end{figure}

\begin{figure}
	\includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/rot_vel_var_vel_0_0g.eps}
    \caption{The evolution of angular velocity at surface (solid line) and the top (dashed line) and bottom (dotted line) limits of the uppermost convective zone, as a function of time for several 1 $M_{\sun}$ models. The models includes PMS rotation with $\Omega / \Omega_{crit}$ values between 0.0084 and 0.0336. The purple star is the surface angular velocity for the present-day Sun \citep{Gill2012}. The dashed vertical lines make reference to the ZAMS.}
    \label{fig:rot_vel_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 30mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/hr_var_vel_0_0g_z1.eps}
    \caption{An example solar 1$M_{\sun}$ grid of stellar evolutionary track from PMS till TAMS covering a wide range of angular velocities. The rotation is activated in the models in the PMS and those models reach before the ZAMS and at a lower $T_{eff}$ than the non-rotating one (solid black line). The luminosity is expressed in terms of $L_{\sun}$.}
    \label{fig:hr_var_vel_0g}
\end{figure}

@@

\begin{figure}
	\includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\columnwidth]{figures/li_var_vel_4_0g.eps}
    \caption{The evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. The models include a magnetic field with an intensity of 4G and PMS rotation with $\Omega / \Omega_{crit}$ between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
    \label{fig:li_var_vel_4_0g}
\end{figure}

@@

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_0_0g.eps}
    \label{fig:subim1}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_3_5g.eps}
    \label{fig:subim2}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_4_0g.eps}
    \label{fig:subim3}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_4_5g.eps}
    \label{fig:subim4}
    \end{subfigure}

    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_5_0g.eps}
    \label{fig:subim5}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 20mm 15mm, clip,width=\textwidth]{figures/li_var_vel_5_5g.eps}
    \label{fig:subim6}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which the magnetic field with intensity has been fixed and $\Omega / \Omega_{crit}$ varies between 0.0084 and 0.0336, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
\label{fig:grid_li_var_vel}
\end{figure*}
\par

\begin{figure*}
    \centering
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0084_var_g.eps}
    \label{fig:subim21}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_014_var_g.eps}
    \label{fig:subim22}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0196_var_g.eps}
    \label{fig:subim23}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_028_var_g.eps}
    \label{fig:subim24}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[trim = 35mm 15mm 15mm 15mm, clip,width=\textwidth]{figures/li_vc_0336_var_g.eps}
    \label{fig:subim25}
    \end{subfigure}
    \begin{subfigure}[h]{0.47\textwidth}
    \includegraphics[width=\textwidth]{figures/blank.eps}
    \label{fig:subim26}
    \end{subfigure}
\caption{Grid showing the evolution of surface \isotope[7]{Li} abundance relative to \isotope[1]{H}, as a function of time for several 1 $M_{\sun}$ models. Each figure shows a set of models in which $\Omega / \Omega_{crit}$ has been fixed and the magnetic field with intensity varies between $3.5\,G$ and $5.5\,G$, respectively. The purple star and square are surface Li abundance for the present-day Sun \citep{Asplund2009} and the Pleiades cluster \citep{Sestito2005} respectively. The dashed lines make reference to the ZAMS.}
\label{fig:grid_li_var_g}
\end{figure*}
